---
title: "Homework 4"
author: "Ankur Bambharoliya and Deeksha Doddahonnaiah"
date: "08/07/2019"
output:
  pdf_document:
    toc: yes
  html_document:
    number_sections: yes
    self_contained: yes
    toc: yes
    toc_float: yes
header-includes:
- \usepackage{amsmath}
- \usepackage{soul}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# CS7290 Causal Modeling in Machine Learning: Homework 4

```{r}
library(png)
library(tidyverse)
library(reticulate)
library(ggplot2)

use_python("/home/d/anaconda3/bin/python3.6")
use_condaenv("ci", required = TRUE)
```

## 1. Necessity and Sufficiency

### 1.1. Probability of Neccessity and Sufficiency

1.1.1 
```{r}
X = c(1,0, 1, 0, 1, 0, 1, 0)
Q = c(0, 0, 1, 1, 0, 0, 1, 1)
X_and_Q = as.integer(X&Q)
ny = c(0, 0, 0, 0, 1, 1, 1, 1)
Y = as.integer(X_and_Q|ny)
print(data.frame(X,Q, ny, Y))
print("After Intervention we have:")
X_new = c(0,0,0,0,0,0,0,0)
Y_new = c(0,0,0,0,1,1,1,1)
print(data.frame(X_new, X, Q, ny, Y, Y_new))

```

From the above table when $X=1$ and $Y=1$, we get the following values  
$n_y = (0,1,1), n_x = 1, n_q = (1, 0, 0)$  
  
After intervention on X $do(X=0)$, $Y=0|do(X=0),X=1, Y=1)$ is satisfied by the following exogenous variables:  
$n_y = 0$, and $n_q = 1$  
  
$P(Y_0=0|X=1, Y=1) = 0.8*0.9 = 0.72$  

1.1.2  

$n_y = (0,0), n_x = 0, n_q = (0, 1)$  
After intervention on X, $do(X=1)$  
$n_y = 0, and n_q = 1$  
$P(Y_1=1|X=0, Y=0) = 0.8*0.9 = 0.72$  

### 1.2 Probability of Neccessity and Sufficiency, and Identifiability

1.2.1
\begin{align*}
PNS = P(y|x) - P(y|x^\prime) \\
0.9198813 - 0.1992071
0.7206742 \\
\end{align*}

1.2.2
\begin{align*}
PN= \frac{PNS} {P(y|x)} \\
=0.7834426 \\
\end{align*}

\begin{align*}
PS= \frac{PNS} {P(y^\prime|x^\prime)} \\
=0.899941 \\
\end{align*}

## 2. Mediation

## 3. Effect of the treatment on the treated 